\section{Building}

In general, ViennaMesh only supports Unix based systems and requires 
several libraries to be available:

\begin{itemize}
   \item CMake~\cite{cmake}
   \item Boost~\cite{boost}
   \item GMP~\cite{gmp}
   \item CGAL~\cite{cgal}
\end{itemize}

Typically, all of those libraries are provided by 
the distributions, for example, Ubuntu. 
%However, CGAL maybe has to be installed manually.

An exemplary build script is provided within the root folder of ViennaMesh. 
\begin{exaipd}
\begin{Verbatim}
build.sh
\end{Verbatim}
\end{exaipd}

Note that \texttt{Debug} and \texttt{Release} builds are available, by utilizing 
the appropriate \texttt{CMake} configuration parameter.
\begin{exaipd}
\begin{Verbatim}
-D CMAKE_BUILD_TYPE=Release
-D CMAKE_BUILD_TYPE=Debug
\end{Verbatim}
\end{exaipd}

If \texttt{Boost} is not available in the usual system paths, the include and 
library paths have to be provided via the 
respective \texttt{CMake} configuration parameters.
\begin{exaipd}
\begin{Verbatim}
-D BOOST_INCLUDEDIR=/path/to/boost/include/
-D BOOST_LIBRARYDIR=/path/to/boost/lib/
\end{Verbatim}
\end{exaipd}

If \texttt{CGAL} is not available in the usual system paths, the include and 
library paths have to be provided via the 
respective \texttt{CMake} configuration parameters.
\begin{exaipd}
\begin{Verbatim}
-D CGAL_INC_DIR=/path/to/cgal/include/
-D CGAL_LIB_DIR=/path/to/cgal/lib/
\end{Verbatim}
\end{exaipd}

By default, the ViennaMesh libraries are built statically. If you want to 
build dynamic libraries, add the following CMAKE parameter:
\begin{exaipd}
\begin{Verbatim}
-DBUILD_SHARED_LIBS=ON
\end{Verbatim}
\end{exaipd}

%Note that the build script expects the parameters \texttt{CGALINC} and 
%\texttt{CGALLIB} to be provided by the environment. 
%Certainly these paths can be entered statically within the build script.

After the build process is finished, the main mesh generation application 
executable is available within the binary folder. 
\begin{exaipd}
\begin{Verbatim}
build/bin/vmesh
\end{Verbatim}
\end{exaipd}

A ViennaMesh application, like \texttt{vmesh}, relies on a set of libraries 
which are generated during the build process of ViennaMesh. These libraries
can be found in the library folder:
\begin{exaipd}
\begin{Verbatim}
build/lib
\end{Verbatim}
\end{exaipd}

This executable is capable of producing volume meshes of high quality of 
\texttt{bnd} and \texttt{hin} input files. 

\TIP{Example input files can be found in the input/ folder.}

A test environment is provided to test the functionality of ViennaMesh. 
A script is available which executes the tests.
\begin{exaipd}
\begin{Verbatim}
tests/run_regression.sh
\end{Verbatim}
\end{exaipd}

